Test susieI using chr17 to 22

### 2020-08-19 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
susieI

Results for each region:
```{r regions}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)
for (i in Niter){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(gene.rpiplist)
}
ngdf
```

>>>>

Results for each region:
```{r regions}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)
for (i in 1:Niter){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(gene.rpiplist)
}
ngdf
```
